Opt-K

### 2013-03-12 paper/paper.tex
added sentence about RMSD
Changed the likelihood equation to make more sense to me. If you don't like it, then switch it back, but more importantly define what you mean by O_{s=0}(x_0).

$$
P[x(t)] dx^N = O_{s=0}(x_0) \prod_{i=0}^{N-1} T(x_i \rightarrow x_{i+1}) \cdot O_{s=i}(x_i)
$$

With a discrete, non-overlapping state space, the likelihood of the
trajectory can be decomposed into a product over the trajectory of two
types of terms: the state to state transition probabilities and the
``emission'' probabilities of each state, the probability of observing a
conformation at a given location in phase space given that the
conformation is within a certain state.

@@

>>>>

$$ 
P[x_t] dx^N = \prod_{i=0}^{N-1} T(x_i \rightarrow x_{i+1}) \cdot \prod_{i=0}^{N} p(x_{i} | \sigma(x_{i}))
$$
%% CRS: I think this is a better way of writing the likelihood
%% This is essentially what Liz Kellogg wrote in her likelihood.

With a discrete, non-overlapping state space, the likelihood of the
trajectory can be decomposed into a product over the trajectory of two
types of terms: the state to state transition probabilities and the
``emission'' probabilities of each state, the probability of observing a
conformation at a given location in phase space given that the
conformation ($x_t$) is within a certain state ($\sigma(x_t)$).

@@

Unfortunately, this doesn't really help with picking the projection operator
to vectorize the conformations (e.g. dihedrals, contact maps, etc). Also,
it's not going to work with RMSD.
